Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-03-12 ident_manu.Rnw
sens evaluation did use surface flux

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux) nor sediment diagenesis.  Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}). A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution. Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

@@

% we use a time series from Weeks Bay NERRS because data are continuous, initial conditions were modified to match weeks bay conditions.  DO time series was filtered to remove tidal advection component and air/sea gas exhange was used.  This is not a perfect example but works for our purposes to demonstrate differeing precision as directly related to identifiability of subsets and paramter types in a subset.  
% note that we are not concerned with the magnitude of the error but the differences in error between parameter subsets and number of runs to convergence.

>>>>

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any advection, mixing, or sediment diagenesis. Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Results are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups given nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIP}). A total of 108 equations are estimated at each time step to return values for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution. Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

@@

% we use a time series from Weeks Bay NERRS because data are continuous, initial conditions were modified to match weeks bay conditions.  DO time series was filtered to remove tidal advection component and air/sea gas exhange was used.  This is not a perfect example but works for our purposes to demonstrate differeing precision as directly related to identifiability of subsets and paramter types in a subset. Thus we were primarily concerned with showing differences in calibration results between paramters sets and not an absolute description of the time series.    
% note that we are not concerned with the magnitude of the error but the differences in error between parameter subsets and number of runs to convergence.

### 2017-03-12 ident_manu.tex
sens evaluation did use surface flux

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Wed Mar 8 10:38:46 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/f654ac2857b352ca61eae17b12e5450b982e6825}{f654ac2857b352ca61eae17b12e5450b982e6825}}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Thu Mar 9 13:12:38 2017 -0600, \href{https://github.com/fawda123/identifiability/commit/70c8da3c6d4aa0e50231198ae90027a250ce2ae5}{70c8da3c6d4aa0e50231198ae90027a250ce2ae5}}
